---
title: "whiskR: An R package for calculating Von Bertanlanffy growth model variables"
output: rmarkdown::html_vignette
authors:  Gary Truong, Ben Walker, Anna Lewis
vignette: >
  %\VignetteIndexEntry{whiskR: An R package for calculating Von Bertanlanffy growth model variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Gary Truong, Ben Walker, Anna Lewis
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

# 1. Introduction

`whiskR` is used for calculating segment lengths of whiskers and working out how many days are represented by each segment. 

The formulas used in the functions are derived from the Von Bertanlanffy growth model equations.

Variables that are used include whisker length, asymptotic length, the growth coefficient k and time.  

# 2. Installation

To install `whiskR` in R:

```{r, eval = F}
# Install pacman 
install.packages("pacman")

pacman::p_load(devtools)

# Install whiskR
devtools::install_github("GaryTruong/whiskR")
library(whiskR)
```

# 3. whiskR functions examples

## 3.1 Calculating *k* (growth coefficient)

```{r, eval = F}
k()
```


## 3.2 Calculating segment length

The LP1() function is used to calculate the specific length of segment required to be in order to obtain a sample that represents a specific amount of time 

L is length
```{r, eval = F}
LP1()

```


## 3.3 Calculating the time represented by a segment

TP1() is used to calculate how much time is represented by a given segment of whisker. 

```{r, eval = F}
TP1()
```


---
title: "whiskR_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{whiskR_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(whiskR)
```
