---
title: "whiskR: An R package for calculating Von Bertanlanffy growth model variables"
output: rmarkdown::html_vignette
authors:  Gary Truong, Ben Walker, Anna Lewis
vignette: >
  %\VignetteIndexEntry{whiskR: An R package for calculating Von Bertanlanffy growth model variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Gary Truong, Ben Walker, Anna Lewis
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

# 1. Introduction

`whiskR` is used for calculating segment lengths of whiskers and working out how many days are represented by each segment. 

The formulas used in the functions are derived from the Von Bertanlanffy growth model equations.

Variables that are used include whisker length, asymptotic length, the growth coefficient k and time. 

The segment() function is used for calculating the sampling sections for a single whisker. It uses the LP1 function in this package using 1 day as the time arrgument as default

# 2. Installation

To install `whiskR` in R:

```{r , eval = F}
# Install pacman 
install.packages("pacman")

pacman::p_load(devtools)

# Install whiskR
devtools::install_github("GaryTruong/whiskR")
library(whiskR)
```

# 3. whiskR functions examples

## 3.1 Calculating *k* (growth coefficient)

```{r, eval = F}
k(L.max, L.asym, Time)

k(L.max = 148.5, L.asym = 150, Time = 365)


```
L.max is the maximum length that the whisker will grow to.
The example provided has a max length of 148.5mm

L.asym is the asymptotic length for that whisker position.
The asymptotic length in the example is 150mm

Time is the time period that the whisker will grow for until it reaches maximum length
The time period for the example given is 365 days.


## 3.2 Calculating segment length

The LP1() function is used to calculate the specific length of segment required to be in order to obtain a sample that represents a specific amount of time 

L is length
```{r, eval = F}
LP1()

```


## 3.3 Calculating the time represented by a segment

TP1() is used to calculate how much time is represented by a given segment of whisker. 

```{r, eval = F}
TP1()
```

## 3.4 Calculating the Maximum Time represented by a whisker

The maxTime() function calculates the maximum time represented by a whisker 

```{r}
maxTime()
```

## 3.5 Generate a table of section represented by a period time of growth

section() uses the LP1 function to generate a table of all of the section lengths corresponding to a specified period time of growth. The default period of time represented is 1 day. A higher number of sections generates samples that approximate the actual time represented by the whisker growth. A fewer number of cuts or higher period of time represented results with an underestimation of the actual time represented by the whisker. 

```{r}
section()
```


